\thesistitle

### 2019-07-29 sections/background.tex
Addressing notes
More colors
T3R

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllll@{}}
\toprule
\rowcolor[HTML]{FFFFFF}
\textbf{Symbol} & \textbf{Meaning} & \textbf{Definition} & \textbf{Description} & \textbf{Properties} \\ \midrule
\rowcolor[HTML]{EFEFEF}
T & Token & - & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code. \\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this token\\spans.\\ \textbf{Category:} Identifier, Keyword,\\Literal, Separator, Operator,\\ Comment or Whitespace.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
N & Node \cite{jiang2007deckard} & Set of tokens. & \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this node\\spans.\end{tabular} \\
\rowcolor[HTML]{EFEFEF}
I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use, roy2007survey}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of cloned\\nodes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{File:} The file in which this\\clone instance is found.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
C & Clone class \cite{bruntink2005use, roy2007survey}& \begin{tabular}[c]{@{}l@{}}Set of clone\\instances.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations. Each of these\\code fragments is called a\\``clone instance''.\end{tabular} & - \\
\rowcolor[HTML]{EFEFEF}
S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\classes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} & - \\
\rowcolor[HTML]{FFFFFF}
%R & Range & A part of a source code file. &  & \begin{tabular}[c]{@{}l@{}}\textbf{Begin line/column:} The line and column at \\ which the range starts.\\ \textbf{End line/column:} The line and column at\\ which the range end.\end{tabular} \\
 \bottomrule
\end{tabular}%
}
\caption{Clone related terminology and how it maps to the source code.}
\label{tab:clone-terminology}
\end{table}

@@

\definecolor{lightyellow}{HTML}{fffdcc}
\definecolor{doublelightyellow}{HTML}{fffa9c}
\newcommand{\highlightYellow}{\makebox[0pt][l]{\color{lightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
\newcommand{\highlightDarkyellow}{\makebox[0pt][l]{\color{doublelightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
\begin{figure}[H]
\begin{parcolumns}{3}
\colchunk[1]{
\begin{javacode}
// File1.java
|\highlightDarkyellow|doA();
|\highlightDarkyellow|doB();
|\highlightYellow|doC();
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// File2.java
|\highlightDarkyellow|doA();
|\highlightDarkyellow|doB();
|\highlightYellow|doC();
\end{javacode}}
\colchunk[3]{
\begin{javacode}
// File3.java
|\highlightYellow|doA();
|\highlightYellow|doB();
doD();
\end{javacode}}
\end{parcolumns}
\caption{Two clone classes: One clone class with three clone instances and one with two clone instances.}
\label{fig:cloneclasses}
\end{figure}

@@

Regarding refactoring, a software system can often not change the source code of its dependencies. This can sometimes be a burden, when an external dependency does not use proper abstractions that are required by a software system. Because of that, in this study, we consider external classes to see what impact they have on the refactoring process.
\simon{Adapter pattern?}

>>>>

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllll@{}}
\toprule
\rowcolor[HTML]{FFFFFF}
\textbf{Symbol} & \textbf{Meaning} & \textbf{Definition} & \textbf{Description} & \textbf{Properties} \\ \midrule
\rowcolor[HTML]{EFEFEF}
T & Token & - & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code. \\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range (R):} The range this token\\spans.\\ \textbf{Category (C):} Identifier, Keyword,\\Literal, Separator, Operator,\\ Comment or Whitespace.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
N & Node \cite{jiang2007deckard} & Set of tokens. & \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range (R):} The range this node\\spans.\end{tabular} \\
\rowcolor[HTML]{EFEFEF}
I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use, roy2007survey}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of cloned\\nodes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{File (F):} The file in which this\\clone instance is found.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
C & Clone class \cite{bruntink2005use, roy2007survey}& \begin{tabular}[c]{@{}l@{}}Set of clone\\instances.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations. Each of these\\code fragments is called a\\``clone instance''.\end{tabular} & - \\
\rowcolor[HTML]{EFEFEF}
S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\classes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} & - \\
\rowcolor[HTML]{FFFFFF}
%R & Range & A part of a source code file. &  & \begin{tabular}[c]{@{}l@{}}\textbf{Begin line/column:} The line and column at \\ which the range starts.\\ \textbf{End line/column:} The line and column at\\ which the range end.\end{tabular} \\
 \bottomrule
\end{tabular}%
}
\caption{Clone related terminology and how it maps to the source code.}
\label{tab:clone-terminology}
\end{table}

@@

\begin{figure}[H]
\begin{parcolumns}{3}
\colchunk[1]{
\begin{javacode}
// File1.java
|\highlightDarkyellow|doA();
|\highlightDarkyellow|doB();
|\highlightYellow|doC();
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// File2.java
|\highlightDarkyellow|doA();
|\highlightDarkyellow|doB();
|\highlightYellow|doC();
\end{javacode}}
\colchunk[3]{
\begin{javacode}
// File3.java
|\highlightYellow|doA();
|\highlightYellow|doB();
doD();
\end{javacode}}
\end{parcolumns}
\caption{Two clone classes: One clone class with three clone instances and one with two clone instances.}
\label{fig:cloneclasses}
\end{figure}

@@

Regarding refactoring, a software system can often not change the source code of its dependencies. This can sometimes be a burden, when an external dependency does not use proper abstractions that are required by a software system. Because of that, in this study, we differentiate between internal and external classes to see what impact they have on the refactoring process.

### 2019-07-29 sections/clonerefactor.tex
T3R

\subsubsection{Convert Equality Array to Graph}
After the global threshold check has failed, we build a clone graph on basis of the equality arrays.

@@

\begin{equation}\label{eq:variabilitycombined}
\frac{|\{(5,6)\}|}{|\{(5,6),(7,7),(8,8),(9,9),(10,10)\}|}*100 = \frac{1}{5}*100 = 20\%
\end{equation}

@@

\begin{equation}\label{eq:variabilitycombined}
\frac{|\{(5,6)\}|}{|\{(1,1),(7,7),(5,6),(7,7),(8,8),(9,9),(10,10)\}|}*100 = \frac{1}{7}*100 = 14\%
\end{equation}

@@

\begin{equation}\label{eq:variabilitycombined}
\frac{|\{(5,6),(11,12),(7,13)\}|}{|\{(1,1),(7,7),(5,6),(7,7),(8,8),(9,9),(10,10),(11,12),(7,13)\}|}*100 = \frac{3}{9}*100 = 33\%
\end{equation}

@@

\subsection{Checking for type 3 opportunities} \label{sec:t3rclonerefactor}
\todo{TODO}

\section{Context Analysis of Clones}\label{chap:contextsetup}
To be able to refactor code clones, CloneRefactor maps the context of code clones. We define the following aspects of the clone as its context:
\begin{enumerate}
  \item \textbf{Relation:} The relation of clone instances among each other through inheritance.
  \item \textbf{Location:} Where a clone instance occurs in the code.
  \item \textbf{Contents:} The statements/declarations of a clone instance.
\end{enumerate}
We define categories for each of these aspects and enable CloneRefactor to determine the catagories of clones.

>>>>

\subsubsection{Convert Equality Array to Graph}
After the global threshold check has failed, we build a clone graph on basis of the equality arrays. The process used for building this graph is the same as the process described in \ref{sec:buildingclonegraph}.

@@

\begin{equation}\label{eq:variabilitycombined1}
\frac{|\{(5,6)\}|}{|\{(5,6),(7,7),(8,8),(9,9),(10,10)\}|}*100 = \frac{1}{5}*100 = 20\%
\end{equation}

@@

\begin{equation}\label{eq:variabilitycombined2}
\frac{|\{(5,6)\}|}{|\{(1,1),(7,7),(5,6),(7,7),(8,8),(9,9),(10,10)\}|}*100 = \frac{1}{7}*100 = 14\%
\end{equation}

@@

\begin{equation}\label{eq:variabilitycombined3}
\frac{|\{(5,6),(11,12),(7,13)\}|}{|\{(1,1),(7,7),(5,6),(7,7),(8,8),(9,9),(10,10),(11,12),(7,13)\}|}*100 = \frac{3}{9}*100 = 33\%
\end{equation}

@@

\subsection{Checking for type 3 opportunities} \label{sec:t3rclonerefactor}
As described in section \ref{sec:type3r}, we define type 3R clones as gapped clones. This means that two existing clones may have a gap of non-gapped clones. We check for every found clone class whether it is a type 3R clone with another clone:

\begin{equation}\label{eq:crtype3r}
\forall (c_1 \in S) \exists (c_2 \in S) x \neq y \land isType3R(c_1, c_2)
\end{equation}

Where \textit{S} is the set of all found clone classes. \textit{$\text{isType3R}(C_1, C_2)$} is a Boolean-valued function that denotes whether two clone classes are type 3R clones of each other. Two clone classes are type 3R clones of each other if each of their instances are within a certain distance of each other:

\begin{equation}\label{eq:istype3r}
\text{isType3R}(C_1, C_2) = \forall (i_1 \in C_1) \exists (i_2 \in C_2) Fi_1 = Fi_2 \land (gap(i_1, i_2) < gap_threshold \lor gap(i_2, i_1) < gap_threshold)
\end{equation}

Where \textit{F} is the file in which the clone instance is located. \textit{gap_threshold} is the defined threshold percentage of the maximum gap size between two clone instances. \textit{$gap(I_1, I_2)$} is the function that calculates the gap between two clone instances.

\section{Context Analysis of Clones}\label{chap:contextsetup}
To be able to refactor code clones, CloneRefactor first maps the context of code clones. We define the following aspects of the clone as its context:
\begin{enumerate}
  \item \textbf{Relation:} The relation of clone instances among each other through inheritance.
  \item \textbf{Location:} Where a clone instance occurs in the code.
  \item \textbf{Contents:} The statements/declarations of a clone instance.
\end{enumerate}
We define categories for each of these aspects and enable CloneRefactor to determine the catagories of clones.
